Towards open collaboration in biomedical and health research: A scoping review

### 2025-01-07 doc/protocol.qmd
chore: :truck: reformat to be a qmd file

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
shorttitle: "Scoping review of open collaboration"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name: Hannah Chatwin
    affiliation: 2
  - name: Mario Garcia
    affiliation: 3
  - name: Daniel Ibsen
    affiliation: 1
  - name: Luke W. Johnston
    affiliation: "1,2"
affiliation:
  - id: 1
    institution: Steno Diabetes Center Aarhus, Denmark
  - id: 2
    institution: Aarhus University, Denmark
  - id: 3
    institution: Copenhagen University, Denmark
output: 
    prereg::prereg_pdf: default
    md_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(stringr)
library(here)
source(here("R/search-terms.R"))
search_terms_inline <- str_replace_all(search_terms$general, "\\*", "\\\\\\*")
```

@@

## Title

`r rmarkdown::metadata$title`

@@

# References

##

```{=tex}
\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}
```
\noindent

>>>>

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
shorttitle: "Scoping review of open collaboration"
date: "2022-11-04"
doi: 10.17605/OSF.IO/K9DR5
execute:
  echo: false
---

```{r setup}
#| include: false
knitr::opts_chunk$set(echo = FALSE)
library(stringr)
library(here)
source(here("R/openalex-search.R"))
search_terms_inline <- glue::glue("({search_terms()$title_search}[title]) AND {search_terms()$general_search}")
```

@@

@@
